Stack Safety is a Security Property

### 2021-04-16 tex/main.tex
Cutting the stack definitions from coroutines

\definition
Let the call-protected set of a context, \(\prot_C(\domMap,\rtm,\yts,\stackid)\),
be the set of components \(\component\) such that
\(\domMap ~ \component = \instack{\stackid}{\sealed{\underscore}}\)
or \(\domMap ~ \component = \instack{\stackid}{\passed{\depth,\depth'}}\) and \(|\rtm ~ \stackid| < \depth\) or
\(|\rtm ~ \stackid| > \depth'\).

\definition
For each of the stepwise, deferred, and observational versions of
stack integrity in the simple model, the equivalent property in the
passing model substitutes the above definitions of \(\context\), initial contexts and update
function, and \(\prot_C\) for their simple equivalents, and is otherwise identical.

@@

@@

Notably, we conjecture that while these systems may implement integrity and confidentiality,
they fall just short of return-to-caller. This is because the standard way to protect returns
in Cheri is to construct {\em return capability}, an object capability that must be invoked
to simultaneously transfer control back to the caller and unseal a capability on an activation
record. An ill-behaved intermediate caller could always pass its caller's return capability on
to its callee instead of its own, ensuring that the callee will return past it. Instead,
we believe that Cheri supports a slightly weaker control-flow property in which only callers
that obey a dynamic reasonableness property are guaranteed not to be skipped.

>>>>

Stack integrity and confidentiality apply in the coroutine model, based on straightforward
projections of each stack's domains, etc. and the machinery of the passing model. We will give
the coroutine-specific properties.

%\definition
%The protected and secret sets of a context as used for calls,
%\(\prot_C(\domMap,\rtm,\yts,\stackid)\) and \(\secret_C(\domMap,\rtm,\yts,\stackid)\),
%are equivalent to their counterparts \(\prot_P\) and \(\secret_P\) applied to a domain map
%that projects out the stack domains of components in stack \(\stackid\) and a
%return target stack \(\rts = \rtm ~ \stackid\). Intuitively, within the active stack we protect
%the same components we would have in the passing model.

%\definition
%For each of the stepwise, deferred, and observational versions of
%stack integrity in the simple model, the equivalent property in the
%passing model substitutes the above definitions of \(\context\), initial contexts and update
%function, and \(\prot_C\) for their simple equivalents, and is otherwise identical.

%\definition \(\MPCT^*\) is now defined as
%\[\begin{aligned}
%\bigcup_{\stackid \in \STACKS,\depth \in \mathbb{Z}} \hspace{-1em} \{\MPCT | \MPCT\langle f_\depth \rangle
%\text{ is a reachable segment}\} \hspace{1em} &
%\text{where } f_\depth ~ (\mach,\pol,(\domMap,\rtm,\yts,\stackid')) \triangleq |\rtm ~ \stackid| \geq \depth \\
%\end{aligned}\]
%and \(\brk{\MPCT}\) similarly projects the depth of the active stack.

%\definition
%For either of the stepwise and observational versions of
%stack confidentiality in the passing model, the equivalent property in the
%coroutine model substitutes the above definitions.

@@

\definition
Let the call-secret set of a context, 
be the set of components \(\component\) such that
\(\domMap ~ \component = \instack{\stackid}{\sealed{\underscore}}\)
or \(\domMap ~ \component = \instack{\stackid}{\passed{\depth,\depth'}}\) and
\(|\rtm ~ \stackid| < \depth\) or \(|\rtm ~ \stackid| > \depth'\).

\definition
Let the yield-secret set of a context, \(\secret_Y(\domMap,\rtm,\yts,\stackid)\),
be the set of components \(\component\) such that
\(\domMap ~ \component = \instack{\stackid'}{\underscore}\) where \(\stackid \not = \stackid`\).

@@
